Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2017-12-29 ms.tex
table

@@

\section{Comparison with Brown Dwarfs and Directly Imaged Companions}
WASP-103b is so highly irradiated that its photospheric temperature ($2000 - 3000$ K) is comparable to that of low mass stars. However, the planet's other properties (surface gravity, rotation rate, irradiation) are different. To explore the effects of varying these parameters, we compared the spectra of WASP-103b to brown dwarfs and young directly imaged companions.

@@

The directly imaged spectra are taken from \cite{2008ApJ...689L.153L}, \cite{2010ApJ...719..497L}, \cite{2010A&A...512A..52B}, \cite{2011ApJ...729..139W} , \cite{2014A&A...562A.127B}, \cite{2011ApJ...730...42L}, \cite{2013ApJ...773...63A}, \cite{2016A&A...587A..56M}, \cite{2013ApJ...772...79A}, and \cite{2008ApJ...673L.185B}. They are calibrated\footnote{Apart for PZ Tel B whose flux calibration is detailed in \cite{2016A&A...587A..56M}.}in absolute flux using published H-band photometry \citep{2008ApJ...689L.153L, 2014A&A...562A.127B, 2011ApJ...729..139W, 2005A&A...430.1027C, 2011ApJ...730...42L, 2013ApJ...773...63A, 2003tmc..book.....C,2009A&A...506..799B} and distances \cite{2016A&A...595A...1G, 2007A&A...474..653V, 1999AJ....117..354D, 1999AJ....117.2381P}, a flux-calibrated spectrum of Vega \citep{1985A&A...151..399M, 1985IAUS..111..225H}, and the corresponding filter passbands.  The brown dwarf spectra \textbf{Jackie: describe catalog of brown dwarf spectra and flux calibration}.

@@

>>>>

\begin{figure}
\includegraphics[width = 0.5\textwidth]{Figures/xsec_FULL.pdf}
\caption{Opacities.}
\label{fig:opacities}
\end{figure}

\subsubsection{Dayside Spectrum}

@@

\section{Comparison with Brown Dwarfs and Directly Imaged Companions}
WASP-103b is so highly irradiated that its photospheric temperature ($2000 - 3000$ K) is comparable to that of low mass stars. However, the planet's other properties (surface gravity, rotation rate, irradiation) are different. To explore the effects of varying these parameters, we compared the spectra of WASP-103b to brown dwarfs and young directly imaged companions. The object properties are summarized in Table\,\ref{tab:sources}.

@@

%TWA 22A - Bonnefoy+2014 (Bonnefoy 09), RXS - Lafren 08,10 (H magfrom Lafren 08), J1610 - Aller+13
%dist: teixeira08, 
The directly imaged spectra are taken from \cite{wahhaj11, aller13, bonnefoy14}. They are calibrated in absolute flux using published H-band photometry \citep{wahhaj11, bonnefoy09, aller13} and distances \citep{gaia16}, a flux-calibrated spectrum of Vega \citep{1985A&A...151..399M, 1985IAUS..111..225H}, and the corresponding filter passbands.  The brown dwarf spectra \textbf{Jackie: describe catalog of brown dwarf spectra and flux calibration}.

@@

\begin{deluxetable*}{llCCCC}
	\tablecolumns{6}
	\tablewidth{0pt}:
	\tablecaption{Source Properties \label{table:sources}}
	\tablehead{
	\colhead{\,} & \colhead{Object} & \colhead{$T_\mathrm{eff}$} & \colhead{logg} & \colhead{H$_2$O A$_1$} & \colhead{H$_2$O A$_2$}}
		\startdata
		Hot Jupiter & W103b night & 1922 \pm 40 & 3.2 \pm 0.04 & 0.07 \pm 1.8\mathrm{e}-01 & -0.00 \pm 1.6\mathrm{e}-01 \\
		\, & W103b quadrature & 2408 \pm 20 & 3.2 \pm 0.04 & -0.14 \pm 7.8\mathrm{e}-02 & -0.01 \pm 6.7\mathrm{e}-02 \\
		\, & W103b dayside & 2982 \pm 10 & 3.2 \pm 0.04 & 0.04 \pm 1.4\mathrm{e}-02 & 0.15 \pm 1.2\mathrm{e}-02 \\
		Brown Dwarf & 2MASS J1320+0409 & 1875 \pm 70 & 5.19 \pm 0.16 & 0.21 \pm 6.3\mathrm{e}-04 & -0.06 \pm 5.0\mathrm{e}-04 \\
		\, & 2MASS J0428-2253 & 2429 \pm 80 & 5.22 \pm 0.09 & 0.16 \pm 1.2\mathrm{e}-04 & -0.03 \pm 1.0\mathrm{e}-04 \\
		\, & 2MASS J0003-2822 & 2889 \pm 80 & 5.18 \pm 0.04 & 0.26 \pm 1.3\mathrm{e}-04 & 0.10 \pm 1.1\mathrm{e}-04 \\
		Imaged Companion & CD-35 2722\tablenotemark{3} & 1800 \pm 100 & 4.5 \pm 0.5 & - & 0.15 \pm 1.0\mathrm{e}-05 \\
		\, & USco 1610-1913B\tablenotemark{2} & 2400 \pm 150 & - & 0.27 \pm 2.0\mathrm{e}-04 & 0.19 \pm 2.2\mathrm{e}-04 \\
		\, & TWA 22A\tablenotemark{3} & 3000 \pm 100 & 4.5 \pm 0.5 & - & 0.29 \pm 2.0\mathrm{e}-05 \\
		\enddata
	\tablenotetext{1}{\cite{wahhaj11}}
	\tablenotetext{2}{\cite{aller13}}
	\tablenotetext{3}{\cite{bonnefoy14}}
	\end{deluxetable*}
